Graphical formalization and automated computing of safety constraints in robotics

### 2012-09-17 paper/Paper.tex
Threw out Fig. 3

\begin{itemize}
	\item Each operator has a different significant visual appearance; in this case we have used color. This kind of classification enables a faster subconscious identification by the user.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appear unnecessarily complex. These operators can be merged (cf.~Fig.~\ref{fig:nested_and}).
\end{itemize}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.4]{and_simplify} %width=0.7\linewidth
  \caption{In order to simplify the appearance of constraints certain operators might be merged. Merged nested \emph{AND} operators (center) are less complex as default ones (left). However nested \emph{AND} operators with mouse over (right) are displayed separated in order to retain full editability.}
  \label{fig:nested_and}
\end{figure}

@@

In order to find a corresponding graphical constraint the sentence has to be analyzed just as you read it. Since ``whenever'' is a semantic equivalent to ``always if'' first of all a \emph{GLOBALLY} operator gets dragged to the dashboard directly followed by an \emph{IF} as shown in figure~\ref{fig:sampleconstraint}. The condition for this \emph{IF} is that there is a pending reminder, so a state ``Not taken yet'' has to be added to the upper bucket of the \emph{IF} operator.
Whenever the just mentioned condition becomes true, there also has to be true in future: Medication is taken properly or caregivers get notified about refuse. Accordingly a \emph{FUTURE} operator containing an \emph{OR} forms the second part of the \emph{IF} operator. Finally two states 'Well done!' and 'Staff notified' get added to the disjunction. The resulting visual constraint can now automatically be translated to the corresponding LTL formula by the editor:

>>>>

\begin{itemize}
	\item Each operator has a different significant visual appearance; in this case we have used color. This kind of classification enables a faster subconscious identification by the user.
	\item The layout of constraints (nested operators) has two dimensions with a certain meaning. Figure~\ref{fig:directions} demonstrates the ``logical'' vertical read direction as well as the time releveant horizontal line.
	\item Multiple nested operators of the same kind which have no order priorities such as \emph{OR} or \emph{AND} appear unnecessarily complex. These operators can be merged.
\end{itemize}

@@

%\begin{figure}[htbp]
  %\centering
  %\includegraphics[scale=0.4]{and_simplify} %width=0.7\linewidth
  %\caption{In order to simplify the appearance of constraints certain operators might be merged. Merged nested \emph{AND} operators (center) are less complex as default ones (left). However nested \emph{AND} operators with mouse over (right) are displayed separated in order to retain full editability.}
  %\label{fig:nested_and}
%\end{figure}

@@

In order to find a corresponding graphical constraint the sentence has to be analyzed just as you read it. Since ``whenever'' is a semantic equivalent to ``always if'' first of all a \emph{ALWAYS} operator gets dragged to the dashboard directly followed by an \emph{IF} as shown in figure~\ref{fig:sampleconstraint}. The condition for this \emph{IF} is that there is a pending reminder, so a state ``Not taken yet'' has to be added to the upper bucket of the \emph{IF} operator.
Whenever the just mentioned condition becomes true, there also has to be true in future: Medication is taken properly or caregivers get notified about refuse. Accordingly a \emph{FUTURE} operator containing an \emph{OR} forms the second part of the \emph{IF} operator. Finally two states 'Well done!' and 'Staff notified' get added to the disjunction. The resulting visual constraint can now automatically be translated to the corresponding LTL formula by the editor:
